Multisymplectic observables and higher Courant algebroids

### 2024-02-28 msgauge-Caprarola.tex
Addendum by MZ.

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[t] % Hybrid format - Title Page
	%
	\begin{center}
	\color{UniGreen}
		\par\noindent\rule{\textwidth}{0.4pt}\\[.5em]	
		{\bf\Large\emph{Multisymplectic observables }}
		\\
		and 
		{\bf\Large\emph{higher Courant algebroids}}\\
		\par\noindent\rule{\textwidth}{0.4pt}			
	\end{center}
	\vfill

@@

\end{frame}
\addtocounter{framenumber}{-1}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}
	Given a \alert{symplectic mfd.} $(M,\omega)$ ...
	\vfill
	\begin{center}
		\includestandalone[width=.95\textwidth]{Pictures/Frame_Embedding_Diagram_symplectic}
	\end{center}
	\vfill
	\begin{minipage}[t][8.5em][t]{\textwidth}
		\only<1-3>{One can naturally associate:}
		\begin{itemize}
			\only<1-3>{
			\item<1-> a \alert<1>{Poisson algebra} w/ $$\{f,g\}_\omega = -\iota_{\vHam_f}\iota_{\vHam_g} \omega$$
			\item<2-> a \alert<2>{(standard twisted) Lie Algebroid};
			\item<3->[-] A Lie algebroid is a "controlled" $\infty$-dimensional Lie algebra w/
			\begin{displaymath}
					\left[\binom{x_1}{f_1},\binom{x_2}{f_2}\right]_\omega
					~=~
					\binom{[x_1,x_2]}{x_1(f_2)-x_2(f_1)-\omega(x_1,x_2)}
				\end{displaymath}
			}
			\item[]<4->
				\quad\\
				\begin{thmblock}[There exists an embedding of Lie algebras.]
					\begin{displaymath}
						\begin{tikzcd}
							\Psi~:&[-1em] (C^{\infty}(M), \{\cdot,\cdot\}_\omega) \ar[r,"\Psi"]& 
							(\Gamma(TM\oplus \mathbb{R}), [\cdot,\cdot]_\omega)
							\\[-2em]
							& f \ar[r,mapsto] & \binom{\mathscr{v}_f}{f}
						\end{tikzcd}		
					\end{displaymath}
				\end{thmblock}
		\end{itemize}
	\end{minipage}
\end{frame}
\note{}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}
	%
	Consider two \alert{gauge-related} symplectic mfd. $(M,\omega)$ and $ (M,\widetilde{\omega})$.
	~~ \alert{($\widetilde{\omega} = \omega - \d B$)}
	%
	\begin{center}
			\includestandalone[width=.8\textwidth]{Pictures/hyb-Frame_BigDiagram_symplectic}
	\end{center}
		\vfill
	\begin{minipage}[t][8em][t]{\textwidth}
		\begin{itemize}
			\only<3-4>{
				\item<3-> There is a natural \alert<3>{isomorphism in the Lie Alg.oids category} \emph{($B$-transformation)}
					\begin{displaymath}
						\binom{x}{f} \mapsto \binom{x}{f-\iota_x B} ~.
					\end{displaymath}~.
				\item<4-> It descends to an \alert<4>{isomorphism of Lie algebras}.
			}
			\only<6-8>{
				\item<6-> \vspace{-2em}Consider an infinitesimal \alert<6>{Hamiltonian group action} $\mathfrak{g}\curvearrowright M$ w.r.t. both $\omega$ and $\tilde{\omega}$.
				\item<7-> let be $f:\mathfrak{g} \to C^\infty(M)_\omega$ and $\tilde{f}:\mathfrak{g} \to C^\infty(M)_{\tilde{\omega}}$ two comoment map s.t.
				\begin{displaymath}
					\tilde{f}(\xi) = f(\xi) - \iota_{\underline{\xi}}B
				\end{displaymath}
				}
			\item[]						
		\end{itemize}
	\only<2>{
		\vspace{-.75em}
		\begin{center}
		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
			\alert{
			\faQuestionCircle \qquad
				{How can we compare the two \emph{observables} algebras?}
			\qquad \faQuestionCircle		
			}
		}
		\end{center}
	}
	\only<5>{
		\vspace{-.75em}
		\begin{center}
		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
			\alert{
			\faQuestionCircle \qquad
				{How can we close the left-hand side?}
			\qquad \faQuestionCircle		
			}
		}
		\end{center}
	}
	\only<8->{
		\vspace{-.75em}
		\tcbset{colback=white,
		colbacktitle=white,
		colframe=red!70!black,
		boxrule=1pt,
		colupper=red!70!black,
		arc=15pt,
		}
		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
			\color{blue}{
			\textbf{Lemma}: The central pentagon commutes!
			}
			\hfill \hyperlink{frame:whyNoVertArrow}{\color{gray}$[>>]$}%\beamerskipbutton{}}
		\end{tcolorbox}
	\vfill

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}\label{frame:pentagonMotivation}
	%
	%Consider two \alert{gauge-related} symplectic mfd. $(M,\omega)$ and $ (M,\widetilde{\omega})$.
	We end up with a pentagonal diagram ...
	%
	\begin{center}
			\includestandalone[width=.8\textwidth]{Pictures/hyb-image_BigDiagram_symplectic}
	\end{center}
	%
	\vfill
	\begin{minipage}[t][8em][t]{\textwidth}
	\centering
	\vspace{-2em}
	\begin{tikzpicture}
		\node [draw,cloud callout,cloud puffs=50,cloud puff arc=100,blue, minimum height=10em,minimum width=35em,callout relative pointer={(-2,-2)}] (L1) {};
		\node [text width=30em,text centered] (L2) {
			\textcolor{blue}{Why should we care about this?}
			\\
			\begin{itemize}
				\item<2->[•] It's a framework for comparing gauge-related observables (same cohomology class).
				\item<3->[•] It has a geometric interpration when $\omega$ \alert{prequantizable}.
				\hfill \hyperlink{frame:pentagonPrequantum}{\color{gray}$[>>]$}%\beamerskipbutton{}}
			\end{itemize}
			\medskip
		};
	\end{tikzpicture}
	\end{minipage}

@@

	%
	\onslide<2>{
		\tikz[overlay,remember picture]
		{
			\node[rounded corners,
                 fill=orange!5,draw=orange!30,anchor=base]
            	 (base) at ($(current page.north east)-(2,1)$) [rotate=-0,text width=3.5cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
		}	
		\begin{tikzpicture}[overlay,remember picture]
		    	\path[->] (base.south east) edge[bend left,red](target.east);
	    \end{tikzpicture}
	}
	%
	\vspace{-1em}
	\begin{columns}[T]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.50\linewidth}
			%
			\centering \it
			$-$ symplectic case $-$
			\onslide<3->{
			\begin{thmblock}[Observables Poisson algebra]
				$C^\infty(M,\omega)$ endowed with
				\vspace{-.5em}
				\begin{displaymath}
					\lbrace \sigma_1, \sigma_2 \rbrace =			
					~ - \iota_{\vHam_1}\iota_{\vHam_2} \omega 
					~= \mathcal{L}_{\vHam_1} \sigma_2
				\end{displaymath}			
				forms a Poisson algebra.
			\end{thmblock}
			}
			%
			\onslide<4->{
			\vspace{1em}
			\begin{itemize}
				\item[\cmark] Skew-symmetric;
				\item[\cmark] multiplication of observables;
				\item[\cmark] Leibniz Rule;
				\item[\cmark] Jacobi equation;
			\end{itemize}		
			}		
		\end{column}	
		%
		\onslide<1->{\vrule{}}
		%
		\begin{column}{.50\linewidth}
			\centering \it
			$-$ $n$-plectic case $-$
			\onslide<5->{			
			\begin{thmblock}[Observables $L_\infty$-algebra]
				$\Omega^{n-1}_{ham}(M,\omega)$ endowed with
				\vspace{-.5em}
				\begin{displaymath}
					\lbrace \sigma_1, \sigma_2 \rbrace =			
					~ - \iota_{\vHam_1}\iota_{\vHam_2} \omega 
				\end{displaymath}			
				can be extended to a \\ $L_\infty-algebra$.
			\end{thmblock}
			}
			%
			\onslide<6->{
			\begin{itemize}
				\item[\cmark] Skew-symmetric;
				\item[\xmark] multiplication of observables;
				\item[\xmark] Jacobi equation;
				%\\ \hspace*{4.25em} full-fledged Jacobi equation;
				\item[\smark] Jacobi equation \emph{up to homotopies}.
			\end{itemize}			
			}
		\end{column}	
	\end{columns}
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{Lie $\infty$-algebra of Observables (higher observables) }
	Let be $(M,\omega)$ a $n$-plectic manifold.
	  	\vfill
	\begin{defblock}[$L_\infty$-algebra of observables ~\emph{(Rogers)} \cite{Rogers2010}]
		\medskip
		\hspace{.25em} Is a cochain-complex $(L,\{\cdot\}_1)$ \\
		\vspace{-1em}
		\begin{center}
			\includestandalone{Pictures/Frame_Observables}
		\end{center}
		\onslide<2->{
			\bigskip
			\hspace{.25em} with $n$ (skew-symmetric) multibrackets $(2 \leq k \leq n+1)$\\
			\vspace{-1em}
			\onslide<3->{
				\begin{center}
					\includestandalone{Pictures/Equation_Multibracket}	
				\end{center}
			}
			\medskip
		}
		%
	\end{defblock}
%	\onslide<3->{
%		\emph{Higher analogue} of the \emph{Poisson algebra structure} associated to a symplectic mfd.
%	\vfill
%	\begin{columns}
%		\hfill
%		\begin{column}{.11\linewidth}	
%			If $n>1$:
%			
%		\end{column}	
%		\begin{column}{.8\linewidth}
%		\begin{itemize}
%			\item[\xmark] \textcolor{red}{we lose} :\quad multiplication of observables, Jacobi equation;
%			%\\ \hspace*{4.25em} full-fledged Jacobi equation;
%			\item[\cmark] \textcolor{green}{we gain} :\quad brackets with arities different than two,\\
%			\hspace*{4.25em}
%			 Jacobi equation \emph{up to homotopies}.
%		\end{itemize}		
%		\end{column}		
%	\end{columns}
%	}
  \end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[t]{Vinogradov Algebroids}
	\begin{defblock}[Vinogradov algebroid (higher Courant)]
		\includestandalone[width=0.95\textwidth]{Pictures/Frame_vinogradov}		
	\end{defblock}
	\vfill
	\begin{itemize}
		\item<6-> $(n=1) ~ \Rightarrow$ standard twisted {\small \color{UniGreen} (by a closed $2$-form)}  \emph{Lie algebroid};
		\item<7-> $(n=2) ~ \Rightarrow$ standard twisted {\small \color{UniGreen} (by a closed $3$-form)} \emph{Courant algebroid};
	\end{itemize}

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{Vinogradov $L_\infty$-algebra}\label{frame:VinoLinfty}
	Vin. alg.oids 
	$\quad\simeq\quad$ 	
	$NQ$-manifolds {\small($L_\infty$-algebroids)}
	$\quad\Rightarrow\quad$ 
	{\small Associated} $L_\infty$-algebra
	%
	\pause
	\begin{defblock}[Vinogradov $L_\infty$-algebra (Zambon) \cite{Zambon2012}]
		\includestandalone[width=0.95\textwidth]{Pictures/Frame_vinogradov-Linfty}	
	\end{defblock}
	\vfill
	\only<6->{
		\tikz[overlay,remember picture]
		{
			\node[rounded corners,
                 fill=gray!1,draw=gray!30,anchor=base]            
            	 (base) at ($(current page.south)+(0,.5)$) [rotate=-0,text width=10cm,align=center] { \footnotesize{\color{gray}{
            	 $e_i = \binom{X_i}{\alpha_i} \in \mathfrak{X}(M)\oplus \Omega^{n-1}(M)$ 
            	 \quad~,\qquad
            	 $f_i \in \bigoplus_{k=0}^{n-2}\Omega^k(M)$.
            	 }}};
		}			
	}
	\hfill \onslide<6->{\hyperlink{frame:VinoDetails}{\color{gray}$[>>]$}}%\beamerskipbutton{}}

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[t]{Comoment maps}
	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  preserving the $n$-plectic form $\omega$,
	\vfill

	\vspace{-1em}
	\begin{columns}[T]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.50\linewidth}
			%
			\centering \it
			\onslide<2->{
				$-$ symplectic case $-$
				\begin{defblock}[Comoment map pertaining to $v$]
					Lie algebra morphism
					$$ f: \mathfrak{g} \to C^\infty(M) $$
					such that
					$$ d~f (x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
				\end{defblock}
			}
		\end{column}	
		%
		\onslide<2->{\vrule{}}
		%
		\begin{column}{.50\linewidth}
			\centering \it
			\onslide<3->{			
				$-$ $n$-plectic case $-$
				\begin{defblock}[Homotopy comoment map \tiny (HCMM)]
					$L_\infty$-morphism 
					$$ (f_k) : \mathfrak{g} \to L_\infty (M,\omega)$$
					such that
					$$ d~f_1(x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
				\end{defblock}	
			}
		\end{column}	
	\end{columns}	
	%
	\pause
	\vfill
	\centering 
	\onslide<4->{\textbf{-- Conserved quantities --}}
	%
	\vspace{-1em}
	\begin{columns}[T]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.50\linewidth}
			%
			\centering \it
			\onslide<4->{
			\begin{propblock}[Noether Theorem]
				\small Fixed $H\in C^\infty_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant) ,
				$$\mathcal{L}_{v_H} f(x) = 0 \qquad \forall x \in \mathfrak{g}$$
			\end{propblock}
			}
		\end{column}	
		%
		\onslide<5->{\vrule{}}
		%
		\begin{column}{.50\linewidth}
			\centering \it
			\onslide<5->{			
			\begin{propblock}[RWZ16 Theorem]
				\small Fixed $H\in \Omega^{n-1}_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant),
				$$\mathcal{L}_{v_H} f_k(p) \in B^k(M) \qquad \forall p \in Z_k(\mathfrak{g})$$			
			\end{propblock}
			}
		\end{column}	
	\end{columns}		
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

>>>>

\usepackage{pdfpages} %copy from other sources

@@

\setbeamercovered{transparent}
%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[t] % Hybrid format - Title Page
	%
	\begin{center}
	\color{UniGreen}
		\par\noindent\rule{\textwidth}{0.4pt}\\[.5em]	
		{\bf\Large\emph{Multisymplectic observables }}
		\\
		and 
		{\bf\Large\emph{higher Courant algebroids}}\\
		\par\noindent\rule{\textwidth}{0.4pt}			
	\end{center}
	\vfill

@@

\end{frame}
\addtocounter{framenumber}{-1}
%-------------------------------------------------------------------------------------------------------------------------------------------------
\setbeamercovered{invisible}

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}
	Given a \alert{symplectic mfd.} $(M,\omega)$ ...
	\vfill
	\begin{center}
		\includestandalone[width=.95\textwidth]{Pictures/Frame_Embedding_Diagram_symplectic}
	\end{center}
	\vfill
	\begin{minipage}[t][8.5em][t]{\textwidth}
		\only<1-3>{One can naturally associate:}
		\begin{itemize}
			\only<1-3>{
			\item<1-> a \alert<1>{Poisson algebra} w/ $$\{f,g\}_\omega = -\iota_{\vHam_f}\iota_{\vHam_g} \omega$$
			\item<2-> a \alert<2>{(standard twisted) Lie Algebroid};
			\item<3->[-] A Lie algebroid is a "controlled" $\infty$-dimensional \alert<3>{Lie algebra} w/
			\begin{displaymath}
					\left[\binom{x_1}{f_1},\binom{x_2}{f_2}\right]_\omega
					~=~
					\binom{[x_1,x_2]}{x_1(f_2)-x_2(f_1)-\omega(x_1,x_2)}
				\end{displaymath}
			}
			\item[]<4->
				\quad\\
				\begin{thmblock}[There exists an embedding of Lie algebras.]
					\begin{displaymath}
						\begin{tikzcd}
							\Psi~:&[-1em] (C^{\infty}(M), \{\cdot,\cdot\}_\omega) \ar[r,"\Psi"]& 
							(\Gamma(TM\oplus \mathbb{R}), [\cdot,\cdot]_\omega)
							\\[-2em]
							& f \ar[r,mapsto] & \binom{\mathscr{v}_f}{f}
						\end{tikzcd}		
					\end{displaymath}
				\end{thmblock}
		\end{itemize}
	\end{minipage}
\end{frame}
\note{}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}
	%
	Consider two \alert{gauge-related} symplectic mfd. $(M,\omega)$ and $ (M,\widetilde{\omega})$.
	~~ \alert{($\widetilde{\omega} = \omega - \d B$)}
	%
	\begin{center}
			\includestandalone[width=.8\textwidth]{Pictures/hyb-Frame_BigDiagram_symplectic}
	\end{center}
		\vfill
	\begin{minipage}[t][8em][t]{\textwidth}
		\begin{itemize}
			\only<3-4>{
				\item<3-> There is a natural \alert<3>{isomorphism in the Lie Alg.oids category} \emph{($B$-transformation)}
					\begin{displaymath}
						\binom{x}{f} \mapsto \binom{x}{f-\iota_x B} ~.
					\end{displaymath}
				\item<4-> It descends to an \alert<4>{isomorphism of Lie algebras}.
			}
			\only<6-8>{
				\item<6-> \vspace{-2em}Consider an infinitesimal \alert<6>{Hamiltonian group action} $\mathfrak{g}\curvearrowright M$ w.r.t. both $\omega$ and $\tilde{\omega}$.
				\item<7-> let be $f:\mathfrak{g} \to C^\infty(M)_\omega$ and $\tilde{f}:\mathfrak{g} \to C^\infty(M)_{\tilde{\omega}}$ two \alert<7>{comoment maps} s.t.
				\begin{displaymath}
					\tilde{f}(\xi) = f(\xi) - \iota_{\underline{\xi}}B
				\end{displaymath}
				}
			\item[]						
		\end{itemize}
	\only<2>{
		\vspace{-.75em}
		\begin{center}
		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
			\alert{
			\faQuestionCircle \qquad
				{How can we compare the two \emph{observables} algebras?}
			\qquad \faQuestionCircle		
			}
		}
		\end{center}
	}
	\only<5>{
		\vspace{-.75em}
		\begin{center}
		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
			\alert{
			\faQuestionCircle \qquad
				{How can we close the left-hand side?}
			\qquad \faQuestionCircle		
			}
		}
		\end{center}
	}
	\only<8->{
		\vspace{-.75em}
		\tcbset{colback=white,
		colbacktitle=white,
		colframe=red!70!black,
		boxrule=1pt,
		colupper=red!70!black,
		arc=15pt,
		}
		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
			\color{blue}{
			\textbf{Lemma}: The central pentagon commutes!
			}
			\hfill \hyperlink{frame:whyNoVertArrow}{\color{gray}$[>>]$}%\beamerskipbutton{}}
		\end{tcolorbox}
	\vfill

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}\label{frame:pentagonMotivation}
	%
	%Consider two \alert{gauge-related} symplectic mfd. $(M,\omega)$ and $ (M,\widetilde{\omega})$.
	We end up with a pentagonal diagram ...
	%
	\begin{center}
			\includestandalone[width=.95\textwidth]{Pictures/hyb-image_BigDiagram_symplectic}
	\end{center}
	%
	\vfill
	\begin{minipage}[t][8em][t]{\textwidth}
	\centering
	\vspace{-2em}
	\begin{tikzpicture}
		\node [draw,cloud callout,cloud puffs=50,cloud puff arc=100,blue, minimum height=10em,minimum width=35em,callout relative pointer={(-2,-2)}] (L1) {};
		\node [text width=30em,text centered] (L2) {
			\textcolor{blue}{Why should we care about this?}
			\\
			\begin{itemize}
				\item<2->[•] It's a framework for comparing gauge-related observables (same cohomology class).
				\item<3->[•] It has a geometric interpration when $\omega$ \alert{prequantizable}.
				\hfill \hyperlink{frame:pentagonPrequantum}{\color{gray}$[>>]$}%\beamerskipbutton{}}
			\end{itemize}
			\medskip
		};
	\end{tikzpicture}
	\end{minipage}

@@

	%
	\onslide<2>{
		\tikz[overlay,remember picture]
		{
			\node[rounded corners,
                 fill=orange!5,draw=orange!30,anchor=base]
            	 (base) at ($(current page.north east)-(2,1)$) [rotate=-0,text width=3.5cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
		}	
		\begin{tikzpicture}[overlay,remember picture]
		    	\path[->] (base.south east) edge[bend left,red](target.east);
	    \end{tikzpicture}
	}
	%
	\vspace{-1em}
	\begin{columns}[T]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.50\linewidth}
			%
			\centering \it
			$-$ symplectic case $-$
			\onslide<3->{
			\begin{thmblock}[Observables Poisson algebra]
				$C^\infty(M,\omega)$ endowed with
				\vspace{-.5em}
				\begin{displaymath}
					\lbrace \sigma_1, \sigma_2 \rbrace =			
					~ - \iota_{\vHam_1}\iota_{\vHam_2} \omega 
					~= \mathcal{L}_{\vHam_1} \sigma_2
				\end{displaymath}			
				forms a Poisson algebra.
			\end{thmblock}
			}
			%
			\onslide<4->{
			\vspace{1em}
			\begin{itemize}
				\item[\cmark] Skew-symmetric brakets;
				\item[\cmark] multiplication of observables;
				\item[\cmark] Leibniz Rule;
				\item[\cmark] Jacobi equation;
			\end{itemize}		
			}		
		\end{column}	
		%
		\onslide<1->{\vrule{}}
		%
		\begin{column}{.50\linewidth}
			\centering \it
			$-$ $n$-plectic case $-$
			\onslide<5->{			
			\begin{thmblock}[Observables $L_\infty$-algebra]
				$\Omega^{n-1}_{ham}(M,\omega)$ endowed with
				\vspace{-.5em}
				\begin{displaymath}
					\lbrace \sigma_1, \sigma_2 \rbrace =			
					~ - \iota_{\vHam_1}\iota_{\vHam_2} \omega 
				\end{displaymath}			
				can be extended to a \\ $L_\infty-algebra$.
			\end{thmblock}
			}
			%
			\onslide<6->{
			\begin{itemize}
				\item[\cmark] Skew-symmetric brackets;
				\item[\xmark] multiplication of observables;
				\item[\xmark] Jacobi equation;
				%\\ \hspace*{4.25em} full-fledged Jacobi equation;
				\item[\smark] Jacobi equation \emph{up to homotopies}.
			\end{itemize}			
			}
		\end{column}	
	\end{columns}
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{Lie $\infty$-algebra of Observables (higher observables) }
	Let be $(M,\omega)$ a $n$-plectic manifold.
	  	\vfill
	\begin{defblock}[$L_\infty$-algebra of observables ~\emph{(Rogers)} \cite{Rogers2010}]
		\medskip
		\hspace{.25em} Is a cochain-complex $(L,\{\cdot\}_1)$ \\
		\vspace{-1em}
		\begin{center}
			\includestandalone[width=0.95\textwidth]{Pictures/Frame_Observables}
		\end{center}
		\onslide<2->{
			\bigskip
			\hspace{.25em} with $n$ (skew-symmetric) multibrackets $(2 \leq k \leq n+1)$\\
			\vspace{-1em}
			\onslide<3->{
				\begin{center}
					\includestandalone{Pictures/Equation_Multibracket}	
				\end{center}
			}
			\medskip
		}
		%
	\end{defblock}
%	\onslide<3->{
%		\emph{Higher analogue} of the \emph{Poisson algebra structure} associated to a symplectic mfd.
%	\vfill
%	\begin{columns}
%		\hfill
%		\begin{column}{.11\linewidth}	
%			If $n>1$:
%			
%		\end{column}	
%		\begin{column}{.8\linewidth}
%		\begin{itemize}
%			\item[\xmark] \textcolor{red}{we lose} :\quad multiplication of observables, Jacobi equation;
%			%\\ \hspace*{4.25em} full-fledged Jacobi equation;
%			\item[\cmark] \textcolor{green}{we gain} :\quad brackets with arities different than two,\\
%			\hspace*{4.25em}
%			 Jacobi equation \emph{up to homotopies}.
%		\end{itemize}		
%		\end{column}		
%	\end{columns}
%	}
  \end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[t]{Vinogradov Algebroids}
	\begin{defblock}[Vinogradov algebroid (higher Courant)]
		\includestandalone[width=0.95\textwidth]{Pictures/Frame_vinogradov}		
	\end{defblock}
	\vfill
	\begin{itemize}
		\item<5-> $(n=1) ~ \Rightarrow$ standard twisted {\small \color{UniGreen} (by a closed $2$-form)}  \emph{Lie algebroid};
		\item<5-> $(n=2) ~ \Rightarrow$ standard twisted {\small \color{UniGreen} (by a closed $3$-form)} \emph{Courant algebroid};
	\end{itemize}

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{Vinogradov $L_\infty$-algebra}\label{frame:VinoLinfty}
	Vin. alg.oids 
	$\quad\simeq\quad$ 	
	$NQ$-manifolds {\small($L_\infty$-algebroids)}
	$\quad\Rightarrow\quad$ 
	{\small Associated} $L_\infty$-algebra
	%
	\pause
	\begin{defblock}[Vinogradov $L_\infty$-algebra (Zambon) \cite{Zambon2012}]
		\includestandalone[width=0.95\textwidth]{Pictures/Frame_vinogradov-Linfty}	
	\end{defblock}
	\vfill
	\only<3->{
		\tikz[overlay,remember picture]
		{
			\node[rounded corners,
                 fill=gray!1,draw=gray!30,anchor=base]            
            	 (base) at ($(current page.south)+(0,.5)$) [rotate=-0,text width=10cm,align=center] {
            	 \footnotesize{\color{gray}{
            	 \onslide<4->{
            	 	$e_i = \binom{X_i}{\alpha_i} \in \mathfrak{X}(M)\oplus \Omega^{n-1}(M)$ 
            	 	\quad~,\qquad
            	 }
            	 $f_i \in \bigoplus_{k=0}^{n-2}\Omega^k(M)$.
            	 }}};
		}			
	}
	\hfill \onslide<6->{\hyperlink{frame:VinoDetails}{\color{gray}$[>>]$}}%\beamerskipbutton{}}

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[t]{Comoment maps}
	Consider a Lie algebra action $\underline{\,\cdot\,}:\mathfrak{g} \to \mathfrak{X}(M)$  preserving the $n$-plectic form $\omega$,
	\vfill

	\vspace{-1em}
	\begin{columns}[T]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.50\linewidth}
			%
			\centering \it
			\onslide<2->{
				$-$ symplectic case $-$
				\begin{defblock}[Comoment map pertaining to $v$]
					Lie algebra morphism
					$$ f: \mathfrak{g} \to C^\infty(M) $$
					such that
					$$ d~f (\xi) = -\iota_{\underline{\xi}} \omega \qquad \forall \xi \in \mathfrak{g}~.$$
				\end{defblock}
			}
		\end{column}	
		%
		\onslide<2->{\vrule{}}
		%
		\begin{column}{.50\linewidth}
			\centering \it
			\onslide<3->{			
				$-$ $n$-plectic case $-$
				\begin{defblock}[Homotopy comoment map \tiny (HCMM)]
					$L_\infty$-morphism 
					$$ (f_k) : \mathfrak{g} \to L_\infty (M,\omega)$$
					such that
					$$ d~f_1(\xi) = -\iota_{\underline{\xi}} \omega \qquad \forall \xi \in \mathfrak{g}~.$$
				\end{defblock}	
			}
		\end{column}	
	\end{columns}	
	%
	\pause
	\vfill
	\centering 
	\onslide<4->{\textbf{-- Conserved quantities --}}
	%
	\vspace{-1em}
	\begin{columns}[T]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.50\linewidth}
			%
			\centering \it
			\onslide<4->{
			\begin{propblock}[Noether Theorem]
				\small Fixed $H\in C^\infty_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant) ,
				$$\mathcal{L}_{\vHam_H} f(\xi) = 0 \qquad \forall \xi \in \mathfrak{g}$$
			\end{propblock}
			}
		\end{column}	
		%
		\onslide<5->{\vrule{}}
		%
		\begin{column}{.50\linewidth}
			\centering \it
			\onslide<5->{			
			\begin{propblock}[RWZ16 Theorem]
				\small Fixed $H\in \Omega^{n-1}_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant),
				$$\mathcal{L}_{\vHam_H} f_k(p) \in B^k(M) \qquad \forall p \in Z_k(\mathfrak{g})$$			
			\end{propblock}
			}
		\end{column}	
	\end{columns}		
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{Gauge related multisymplectic manifolds and comoment maps}
	Consider $M$ smooth mfd.
	%
	\begin{defblock}[Gauge related $n$-plectic structures]
		\bigskip
		\begin{columns}[T]
			\setlength{\belowdisplayskip}{5pt}
			\begin{column}{.50\linewidth}
				%
				\centering \it
				$\quad\omega,~ \tilde{\omega}~ \in \Omega^{n+1}(M)$ multisymplectic,
			\end{column}	
			%
			\begin{column}{.50\linewidth}
				\centering \it
				such that $\omega = \tilde{\omega} - d B$
			\end{column}	
		\end{columns}	
		\bigskip	
	\end{defblock}
	%
	\pause
	\vfill
	\par\noindent\rule{\textwidth}{0.4pt}	
	\vfill
	%
	Consider \quad $\underline{\,\cdot\,} : \mathfrak{g} \to \mathfrak{X}(M)$ preserving $\omega$ and $\tilde{\omega}$,
	%\phantom{consider}\quad $\mathcal{L}_{v_\xi}\omega=\mathcal{L}_{v_\xi}\tilde{\omega} = 0 \quad \forall \xi \in \mathfrak{g}$
	\\
	let \qquad$f: \mathfrak{g}\to L_\infty(M,\omega)$ an \emph{homotopy comoment map} ~ w.r.t. $\mathfrak{g}\curvearrowright (M,\omega)$
	\pause
	\begin{lemblock}[Also $(M,\tilde{\omega})$ admits HCMM $(\tilde{f})$]
		\medskip
		\begin{columns}
			\begin{column}{.325\linewidth}
					\onslide<4->{
						\begin{displaymath}
							\tilde{f}_k = f_k +	
								\tikz[baseline,remember picture]{\node[rounded corners,
	                        		fill=blue!5,draw=blue!30,anchor=base]            
	            					(target) {$\mathrm{b}_k$ };
	            					}	
						\end{displaymath}
					}		
			\end{column}
			\begin{column}{.625\linewidth}	
					\onslide<4->{
						\begin{displaymath}
						%
						\begin{tikzcd}[baseline=(O.base),ampersand replacement=\&]
							|[alias=O]| 
							\tikz[baseline,remember picture]{\node[rounded corners,
	                        		fill=blue!2,draw=blue!30,align=center]            
	            					(base) {$\mathrm{b}_k$};}						
							~:\&[-3em] \Lambda^k\mathfrak{g} \ar[r]\& \Omega^{n-k}(M)
							\\[-2em]
							\& \xi_1\wedge\dots \xi_k \ar[r,mapsto] \&
							(-)^k \iota(\underline{\xi_1})\dots \iota(\underline{\xi_{x_k}}) B
						\end{tikzcd}		
						\end{displaymath}								
					}		
			\end{column}
		\end{columns}
		\bigskip
		\only<4->{
			\begin{tikzpicture}[overlay,remember picture]
			    	\path[->,opacity=0.3] (base.west) edge[bend left,blue](target.south east);
		    \end{tikzpicture}		
	    }
	\end{lemblock}
	%
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------
